\addchapheadtotoc
\chapter{Conclusions and future work}~\label{chapter:conclusion}

\section{Summary of findings}
%Thermal radiation can be a significant heat transfer mechanism in combustion systems. A brief overview of the fundamentals of radiation, as well as categorized effects of radiation in combustion specifically, were discussed in Chapter~\ref{chapter:Importance}. 
%Radiation has been shown to contribute significantly to changes in the fluid dynamics, boundary interactions, and chemical characteristics in and around the flame.
%%Radiation acts as a diffusive process of thermal energy, where high temperature and opaque regions emit strongly to the medium and surroundings. 
%Radiation tends to reduce peak flame temperatures that may stymie combustion, reduce buoyant forces in the flame.
%Overall, radiative source and sink terms in participating gas medium tend to be less than heat release from combustion reactions. As a result, the contribution of radiation is more meaningful across long timescales compared to the fast chemistry. Therefore, an understanding of slow processes like chemical production of pollutants NO$_x$ and soot require accurate modeling of radiation.

%In propulsion combustors, the exact role of radiation remains poorly understood. Previous studies suggest radiative emission from aeronautical gas-turbines can contribute an identical order of magnitude heat flux to the boundaries as convective heat transfer. Some studies have demonstrated peak temperature reductions of up to 200K when radiation is introduced, while others have shown temperature increases resulting from improved combustion in highly-absorbing regions. Overall analysis shows as much as 80\% of the radiative emission in fuel-rich zones is from soot. Rocket engines exhibit between 5\% and 30\% of overall heat flux to the walls resulting from radiative emission, largely located near the nozzle throat where temperatures are the highest.
%Radiation is also significant in wild-fires and other hazardous combustion scenarios. Heat flux can propagate a large distance from the flame and ignite nearby objects, leading to fire spread.

%The background of the Monte Carlo method of modeling radiation is next discussed in Chapter~\ref{chapter:Modeling}. 
%A GPU-accelerated Monte Carlo ray tracing solver is constructed and verified in this study. 
The Monte Carlo method is broadly known to be the most accurate, robust, but also one of the most computationally expensive radiation models.
However, with rapid development of computing hardwares, it has been used more frequently and recognized to be a promising alternative for coupled combustion simulations in the future.
%First, 
The fundamentals of MCRT, including the random number relations of point of emission, direction and wavenumber for forward Monte Carlo ray tracing is discussed in detail in this thesis.
A description of the tracing procedure through the mesh and to the boundaries is provided.
Several alternative mathematical techniques, as well as re-formulations of the Monte Carlo ray tracing method are presented, along with their various advantages. 

Inspired by the recent development of computer graphics, including the usage of Graphics Processing Unit (GPU) and the algorithm of Bounding Volume Hierarchy (BVH), 
previous literature is reviewed on applications of these methods to ray tracing. It is found that the few studies that have applied GPUs to MCRT for thermal radiation modeling observed tremendous runtime reductions, and that no existing studies have leveraged the BVH algorithm in the calculation of a radiatively participating medium.

Based on these understandings, 
%Finally, a description of the radiation implementation for this research is presented, 
a MCRT-based radiation solver is constructed using both GPUs and BVHs, for a robust tracing procedure through an unstructured polyhedral mesh. A high fidelity line-by-line spectral model is also incorporated to allow for accurate non-gray modeling.
The solver is integrated with the \verb|OpenFOAM| CFD software package, which enables its use with coupled, transient combustion simulations through a source term contribution to the energy equation. Additionally, the Kokkos programming model and ArborX geometric search library are used for interchangeable GPU/CPU compatibility and scalable BVH implementation, respectively. Three primary ray tracing implementations are presented: Standard-Forward, ArborX-Reverse, and Hybrid-Reverse. Each offers a different approach to ray tracing, utilizing standard forward ray tracing, BVH-based reverse ray tracing, and a combination of both, respectively. A novel distributed ray tracing procedure, where rays are emitted and traced across multiple MPI ranks simultaneously, is presented for use with both ArborX-Reverse and Hybrid-Reverse to improve performance in high performance computing systems.

The present solvers are verified using three geometries of varying complexity: a one-dimensional plane-parallel participating medium, a three-dimensional vitiated backward-facing step combustor, and a DNS of a small turbulent pool fire. Frozen field analyses were conducted for all of these configurations. Additionally, the solver is applied to a LES of a larger turbulent pool fire, to demonstrate its applicability in coupled combustion simulations.

% Plane-parallel
One dimensional plane-parallel results compare excellently against exact solutions for all three primary versions of the solver. Tests are conducted for a variety of absorption coefficients, medium temperatures, and ray counts.
Radiative absorption increased with absorption coefficient and temperature, and stochastic variability becomes more apparent with lower ray-counts.
ArborX-Reverse and Hybrid-Reverse tracing methods demonstrate increased variance near the boundaries and for lower absorption coefficients due to greater numbers of reverse-rays exiting the domain.
The solvers demonstrated small differences in runtime performance for all configurations, and results compare equally well when run with eight MPI ranks.

% Backward Facing step
For the 3-D backward-facing step combustor,
%is simulated at a moderate temperature of approximately $800$K. 
results are compared against those of an established Fortran-radiation solver as a further verification. Excellent agreement is obtained between the two solvers. It is found that GPU parallel processing reduces runtimes by approximately two orders of magnitude.
% The speedups are a result of two advancements: improvements in parallel implementation through the introduction of the Kokkos back-end, and improved memory management through minimal duplication of mesh-data within the CPU.

% DNS POOL FIRE:
The previous two configurations involve only gray media, while the 3-D DNS of a small pool-fire flame is employed to further verify the implementation of the line-by-line database. Runtimes for various parallel back-ends including GPU, CPU, and serial are compared. Both NVIDIA V100 and NVIDIA A100 GPUs are shown to accelerate the solver over two orders of magnitude, with the A100 showing almost 400 times speedup. OpenMP parallel execution also shows an order of magnitude speedup over serial. To faciliate comparison with two OpenFOAM stock solvers, radiation is simulated again using a uniform-absorption coefficient gray model, and compared amongst the MCRT, fvDOM and P1 solvers. fvDOM is shown to have reasonably good accuracy while P-1 deviates significantly from baseline MCRT results. Meanwhile, the GPU-accelerated MCRT solver is shown to run faster than both serial fvDOM and serial P-1 radiation solutions within a gray medium, indicating its great potential to replace these solvers in time-accurate combustion simulations.

% TRANSIENT POOL FIRE:
Lastly, a similar turbulent pool fire is simulated from its initial conditions in a transient simulation.
Results show a significant decrease in temperature of up to $600$ K compared to the simulation without radiation.
%First, a frozen-field analysis is conducted on an early time-step of the simulation. Results show a strong redistribution of energy throughout the flame and to the surrounding walls. Trends between radiative absorption and emission with the Planck-mean absorption coefficient and flame temperature are outlined. A minimal degree of radiative absorption is seen in the surrounding medium. Additionally, the radiative re-absorption in the flame increased considerably when the line-by-line non-gray model was implemented. 
Detailed account of runtime consumption in the solver within one timestep is described through the use of a Kokkos profiling tool~\cite{Trott_KokkosEcosystem2021}. It is found that a significant portion of the runtime is consumed through the loading and transferal of the line-by-line database. These results were magnified for the GPU, where several deep copies of CPU to GPU memory must be performed.
%Results and performance are then presented considering all timesteps in the run. Interpretability of the physical effects on the pool flame were expected to be more accurate because coupled influences of radiation can only be accounted for by simulating from initial conditions. 
 Profiling results display a consistent $25$\% of the runtime was consumed by radiation for each time-step, on average. Noting the results from the profiling of the frozen-field analysis, it was predicted that the consumption in runtime would decrease if the mesh and non-gray information are maintained in memory between time-steps, which is recommended as an immediate future development.

% Finally, succesful validation of the present radiation model encouraged the modeling of a Pratt \& Whitney NEO combustor with line-by-line accurate non-gray modeling. A scatter diagram of various computational parameters in the medium revealed soot exerted a controlling influence on the radiation emission characteristics in the flame. At temperatures beyond a crossover point, soot volume fractions diminished rapidly, resulting in an equally rapid decrease in radiative emission, leading to a local maximum in radiative emission as a function of temperature. The boundaries of the combustor displayed a much higher degree of radiative heat flux adjacent to the fuel-rich region of the combustor. The influence of non-gray modeling was then presented. The line-by-line non-gray model as shown to increase radiative re-absorption significantly and decrease wall-incident radiative heat flux by up to $60$\%. The contributions of various chemical species to the wall-incident heat flux was evaluated, and it was found that soot contributed the most, followed by CO$_2$. 
% Profiling of the radiation model on the combustor showed a reduction of runtime by approximately 75\%, and the non-gray calculation increased runtimes by 10\%.

\section{Recommendations for Future Work}
The present implementation of MCRT with GPUs has shown significant speedup compared to CPU implementations. However, it is anticipated that further speedups can be obtained by implementing improved GPU-favorable memory coalescence and by sorting rays by absorption coefficient~\cite{Silvestri2019ASimulation}.
Furthermore, a fully asynchronous computation of radiation and CFD on the GPU and CPU simultaneously would reduce the apparent runtime of radiation to only the communication time between the two. The potential for the Bounding Volume Hierarchy was limited in the present demonstration, however, the BVH may have potential to provide improvements for a larger distributed-memory simulations.
Null-collision Monte Carlo has demonstrated significant potential to accelerate MCRT. Combining this method with advanced mesh approaches, such as the BVH, could bring measurable speedups to the ray-tracing calculation.
Improvements such as these, along with those presented in this thesis, will enable scientists and engineers to have more complete understanding of the influence of radiation within their combustion systems. 